---
title: "Map of IMR locations Bergen"
author: "Christian Andersen"
date: "27 9 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stringr)

# install.packages("leaflet")
library(leaflet)
```

## Introduction

This is my delivery to the Assignment R Markdown and leaflet. It shows the location of buildings at the Institute of Marine Research, Bergen, Norway.

## Defining content of the map
First I define the logo to be used as marker in the map. After that the popup text is defined.

```{r def, echo=TRUE}
logo <- makeIcon(iconUrl="G:/Kostnadsanalyse og prising/R kurs/Coursera Data Science/IMR_logo.png",
                 iconWidth = 35, iconHeight = 35, iconAnchorX = 17.5, iconAnchorY = 17.5)
site <- c("Main building, Nordnesgaten 50", "Offices, Nordnesgaten 33","New offices, Strandgaten 196","Shipping department, Nykirkekaien")
```

## Creating the map
First the location of the four buildings is defined. Then the map is created.

```{r map, echo=TRUE}
loc <- data.frame(lat=c(60.4,60.3992,60.3982,60.3975),lng=c(5.3035,5.308,5.3101,5.314))
loc %>% leaflet() %>% addTiles() %>% addMarkers(icon=logo, popup=site) 
```


